### 2021-06-10 paper/appendix_data.tex
Start on educ rapid test section.

\subsection{Assortative Matching}

@@

For the last group of contacts which cover things like leisure activities, grocery
shopping etc. we have no reliable data by how much policies reduce them. In addition,
they are likely to be affected by social and psychological factors such as pandemic
fatigue and vacations. Because of this we estimate them like the infection probabilities
to fit the time series data. We use very few change points and tie them to particular
events such as policy announcements or particular holidays.

@@

For work contacts, we know from the COSMO study (\cite{Betsch2021}, 20th/21st of April)
that 60\% of workers who receive a test offer by their employer regularly use it. We
assume this to be time constant.

In addition, there are some surveys that allow us to trace the expansion of employers
who offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported
being offered weekly rapid tests by their employer \citep{Ahlers2021}. This share
increased to 60\% until the first days of April \cite{ZDF2021}. Until mid April 70\% of
workers were expected to receive a weekly test offer \citep{AerzteZeitung2021}. However,
according to surveys conducted in mid April \citep{Betsch2021}, less than two thirds of
individuals with work contacts receive a test offer. Starting on April 19th employers
were required by law to provide two weekly tests to their employees
\citep{Bundesanzeiger2021}. We assume that compliance is incomplete and only 80\% of
employers actually offer tests.

@@

@@

We assume that employees in educational facilities start getting tested in 2021 and that
by March 1st 30\% of them are tested weekly. The share increases to 90\% for the week
before Easter. At that time both Bavaria and Baden-Württemberg were offering tests to
teachers and North-Rhine Westphalia and Lower Saxony were already testing students and
tests for students and teachers were already mandatory in Saxony. After Easter we assume
that 95\% of teachers get tested twice per week.

>>>>

\subsection{Contacts by age}

@@

For both work and school contacts we assume that starting November with the lockdown
light in Germany, hygiene measures (such as masks, ventilation and hand washing) became
more strict and more conscientiously observed, leading to a reduction of 33\% in the number of contacts with the potential to transmit Covid-19.

For the last group of contacts which cover things like leisure activities, grocery
shopping etc. we have no reliable data by how much policies reduce them. In addition,
they are likely to be affected by social and psychological factors such as pandemic
fatigue and vacations. Because of this we estimate them like the infection probabilities
to fit the time series data. We use very few change points and tie them to particular
events such as policy announcements or particular holidays.\comment[id=K]{@Janos should we already add in numbers in here?}

@@

For work contacts, we know from the COSMO study (\cite{Betsch2021}, 20th/21st of April)
that 60\% of workers who receive a test offer by their employer regularly use it. We
assume this share to be time constant.

In addition, there are some surveys that allow us to trace the expansion of employers who
offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported being
offered weekly rapid tests by their employer \citep{Ahlers2021}. This share increased to
60\% until the first days of April \cite{ZDF2021}. Until mid April 70\% of workers were
expected to receive a weekly test offer \citep{AerzteZeitung2021}. However, according to
surveys conducted in mid April \citep{Betsch2021}, less than two thirds of individuals
with work contacts receive a test offer. Starting on April 19th employers were required
by law to provide two weekly tests to their employees \citep{Bundesanzeiger2021}. We
assume that compliance is incomplete and only 80\% of employers actually offer
tests.\comment[id=HM]{Can we use the IZA/BMAS survey? Not sur about citing evening news
in scientific papers.}\comment[id=K]{I am not aware of any survey looking at compliance.
If you know of some, that would be great. Updating this might change our results but it
would definitely be an improvement!}

@@

We assume that employees in educational facilities start getting tested in 2021 and that
by March 1st 30\% of them are tested weekly.

The share increases to 90\% for the week before Easter. At that time both Bavaria
\citep{BayrischerRundfunk2021} and Baden-Württemberg \citep{MinisteriumKultus2021} were
offering tests to teachers and North-Rhine Westphalia \cite{DPA2021} and Lower Saxony
\citep{SueddeutscheZeitung2021} were already testing students and tests for students and
teachers were already mandatory in Saxony \citep{SueddeutscheZeitung2021a}. After Easter
we assume that 95\% of teachers get tested twice per week.\comment[id=K]{Mostly newspaper
articles and one KuMi press communication. I have more sources for the smaller federal
states but they are extremely time consuming to enter into the references.}

% --------------------------------------------------------------------------------------
%
%def _add_educ_rapid_test_fade_in_params(params):
%    """Add the shares how many people with educ contacts get a rapid test.
%
%    Sources:
%        - 17-24 of March 2021 (Mon, 2021-03-22):
%            - NRW had 80% tests for students before Easter (https://bit.ly/3u7z8Rx)
%            - BY: test offers to educ_workers (https://bit.ly/3tbVX5u)
%            - BW: only tests for educ workers (https://bit.ly/2S7251M)
%
%            - federal level:
%                "In Kitas und Schulen sollen die Testmöglichkeiten "mit der
%                steigenden Verfügbarkeit von Schnell- und Selbsttests"
%                ausgebaut werden" (https://bit.ly/3nuCSKi)
%            - Some KiTa workers are being tested (https://bit.ly/3nyGyus)
%            - Self tests for students in Berlin (https://bit.ly/2ScGu8m)
%            - Schleswig-Holstein: test offer (https://bit.ly/3eVfkuv)
%            - mandatory tests in Saxony (https://bit.ly/3eEQGhn)
%            - no tests yet for students in Hessia, but already ordered
%              (https://bit.ly/3gMGJB4)
%            - Niedersachsen had one test week before Easter (https://bit.ly/3gOOC96)
%
%            => assume 90% of teachers and 40% of students do rapid tests
%
%        - After Easter (2021-04-07):
%            - NRW: tests are mandatory for all
%            - Bavaria: tests are mandatory for all (https://bit.ly/3nz5fXS,
%              https://bit.ly/2QHilX3)
%            - BW: voluntary tests for students (https://bit.ly/3vuetaD)
%            - Brandenburg starts with tests (https://bit.ly/3xAihZB)
%            - Schleswig-Holstein: mandatory tests (https://bit.ly/3eVfkuv)
%
%            => assume 95% of teachers and 75% of students get tested
%
%        - BW: tests mandatory starting 2021-04-19 (https://bit.ly/3vuetaD)
%
%            => assume 95% of teachers and 95% of students get tested
%
%    """
%    params = params.copy(deep=True)
%
%    loc = ("rapid_test_demand", "educ_worker_shares")
%    params.loc[(*loc, "2020-01-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-01-01"), "value"] = 0.0
%    # this is arbitrary to have a more convex shape
%    params.loc[(*loc, "2021-03-01"), "value"] = 0.3
%    params.loc[(*loc, "2021-03-22"), "value"] = 0.9
%    params.loc[(*loc, "2021-04-07"), "value"] = 0.95
%    params.loc[(*loc, "2021-04-19"), "value"] = 0.95
%    params.loc[(*loc, "2021-06-01"), "value"] = 0.95
%    params.loc[(*loc, "2025-12-31"), "value"] = 0.95
%
%    loc = ("rapid_test_demand", "student_shares")
%    params.loc[(*loc, "2020-01-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-02-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-03-01"), "value"] = 0.1
%    params.loc[(*loc, "2021-03-22"), "value"] = 0.4
%    params.loc[(*loc, "2021-04-07"), "value"] = 0.75
%    params.loc[(*loc, "2021-04-19"), "value"] = 0.95
%    params.loc[(*loc, "2021-06-01"), "value"] = 1.0
%    params.loc[(*loc, "2025-12-31"), "value"] = 1.0
%
%    # Assume weekly tests before Easter and twice weekly tests after Easter
%    # We should get a fade-in through different ends of Easter vaccation
%    params.loc[("rapid_test_demand", "educ_frequency", "before_easter"), "value"] = 7
%    params.loc[("rapid_test_demand", "educ_frequency", "after_easter"), "value"] = 3
%
%    return params
%
% --------------------------------------------------------------------------------------

@@
